\textbf{Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata}

### 2023-04-17 manuscript_v3/main.tex
Fixed model, discussion, appendix

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

The COVID-19 pandemic continues to be a worldwide public health concern.
Although vaccines against this disease were rapidly developed,
vaccination uptake has not ben equal across all the segments of the
population. In particular, it has been shown that there have been
differences in vaccine uptake across different segments of the
population. However, there are also differences in vaccination across
geographical areas, which might be important to consider in the
development of future public health policies against COVID-19. In this
study, we examined the relationship between vaccination status (having
received the first dose of a COVID-19 vaccine), and different
socio-economic and geographical factors. Our results show differences in
vaccination due to race/ethnicity, income, Health Regions (geographical
areas used for health service access in Ontario), and their
interactions. In particular, we show that individuals who identified as
Arab/Middle Eastern, Black, or Latin American, had significantly lower
odds of vaccination than White/Caucasian individuals (ORs=0.31, 0.32,
0.28, and \emph{p}=0.004, \emph{p}\textless0.001 and \emph{p}=0.004,
respectively), and that individuals with a household income below CAD
25,000 who identified as Arab/Middle Eastern (OR=3.05, \emph{p}=0.013),
Black (OR=3.19, \emph{p}=0.004), Latin American (OR=2.80,
\emph{p}=0.041), or that belonged to other minority groups (OR=4.59,
\emph{p}\textless0.001) had higher odds of vaccination than individuals
from the same racial/ethnic group in higher income brackets. Finally, we
also identified lower odds of vaccination within certain minority groups
in the West Health Region, which comprises the regions of Waterloo and
Niagara, the counties of Wellington, Essex and Lambton, and the cities
of Hamilton, Haldimand, Brant, and Chatham-Kent. This study shows that
there is an ongoing need to better understand and address differences in
vaccination uptake across diverse segments of the population that have
been largely impacted by the pandemic.

@@

Within the age groups of survey respondents, the age group between 16-34
years had the highest representation in the survey responses (1,520 or
42.8\% of all responses). Within this age bracket, 73\% of respondents
indicated having received the vaccine, whereas the lowest vaccination
rate was in the bracket of those 55 years of age and above, with 72\%.
The Health Region with highest representation in the survey was Toronto,
accounting for 1,323 entries (37.3\% of the total), with a vaccination
rate of 72\%. Regarding race/ethnicity, individuals that identified as
White/Caucasian represented 37\% of all entries (1,312) and had the
highest vaccination uptake with 82\% of them indicating to have received
the COVID-19 vaccine. On the other hand, the ethnic group with the
lowest number of entries in the survey was Latin American, with a total
of 180, or 5\% of all entries. Vaccination rates across all minority
groups were below the value reported by White/Caucasians, with the
lowest vaccination rate (60\%) being reported by individuals that
identified as Indigenous.

\begin{verbatim}
Warning: Outer names are only allowed for unnamed scalar atomic inputs
\end{verbatim}

@@

\begin{tabular}{lcc}
\toprule
\textbf{Variable} & \textbf{no}, N = 958 & \textbf{yes}, N = 2,591\\
\midrule
\textbf{Income} &  & \\
\hspace{1em}60000\_and\_above & 305 (23\%) & 1,048 (77\%)\\
\hspace{1em}25000\_59999 & 253 (28\%) & 636 (72\%)\\
\hspace{1em}under\_25000 & 400 (31\%) & 907 (69\%)\\
\textbf{Age Group} &  & \\
\hspace{1em}16\_34 & 409 (27\%) & 1,111 (73\%)\\
\hspace{1em}35\_54 & 252 (26\%) & 712 (74\%)\\
\hspace{1em}55\_and\_over & 297 (28\%) & 768 (72\%)\\
\textbf{Health Region} &  & \\
\hspace{1em}Toronto & 371 (28\%) & 952 (72\%)\\
\hspace{1em}Central & 224 (28\%) & 580 (72\%)\\
\hspace{1em}East & 135 (23\%) & 448 (77\%)\\
\hspace{1em}West & 228 (27\%) & 611 (73\%)\\
\textbf{Month} &  & \\
\hspace{1em}October & 469 (27\%) & 1,263 (73\%)\\
\hspace{1em}November & 376 (28\%) & 980 (72\%)\\
\hspace{1em}December & 113 (25\%) & 348 (75\%)\\
\hspace{1em}September & 0 (NA\%) & 0 (NA\%)\\
\textbf{Race} &  & \\
\hspace{1em}white\_caucasian & 233 (18\%) & 1,079 (82\%)\\
\hspace{1em}arab\_middle\_eastern & 76 (36\%) & 138 (64\%)\\
\hspace{1em}black & 114 (38\%) & 184 (62\%)\\
\hspace{1em}east\_asian\_pacific\_islander & 69 (23\%) & 234 (77\%)\\
\hspace{1em}indigenous & 76 (40\%) & 115 (60\%)\\
\hspace{1em}latin\_american & 69 (38\%) & 111 (62\%)\\
\hspace{1em}mixed & 105 (34\%) & 205 (66\%)\\
\hspace{1em}other & 128 (35\%) & 239 (65\%)\\
\hspace{1em}south\_asian & 88 (24\%) & 286 (76\%)\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\end{tabular}
\endgroup{}
\end{table}

@@

\hspace{1em}16\_34 & — & — &  & — & — & \\
\hspace{1em}35\_54 & 0.93 & 0.77, 1.14 & 0.5 & 0.90 & 0.67, 1.21 & 0.5\\
\hspace{1em}55\_and\_over & 0.74 & 0.61, 0.89 & 0.002 & 0.99 & 0.74, 1.32 & >0.9\\

@@

\textbf{Income} &  &  &  &  &  & \\
\hspace{1em}60000\_and\_above & — & — &  & — & — & \\
\hspace{1em}25000\_59999 & 0.59 & 0.41, 0.84 & 0.003 & 0.59 & 0.39, 0.88 & 0.010\\
\hspace{1em}under\_25000 & 0.41 & 0.29, 0.58 & <0.001 & 0.37 & 0.25, 0.56 & <0.001\\

@@

\hspace{1em}white\_caucasian & — & — &  & — & — & \\
\hspace{1em}arab\_middle\_eastern & 0.24 & 0.12, 0.49 & <0.001 & 0.31 & 0.14, 0.68 & 0.003\\
\hspace{1em}black & 0.30 & 0.17, 0.54 & <0.001 & 0.32 & 0.17, 0.60 & <0.001\\
\hspace{1em}east\_asian\_pacific\_islander & 0.73 & 0.36, 1.51 & 0.4 & 1.15 & 0.50, 2.66 & 0.7\\
\hspace{1em}indigenous & 0.38 & 0.17, 0.82 & 0.014 & 0.45 & 0.20, 1.04 & 0.061\\
\hspace{1em}latin\_american & 0.28 & 0.13, 0.59 & <0.001 & 0.27 & 0.11, 0.66 & 0.004\\
\hspace{1em}mixed & 0.58 & 0.30, 1.11 & 0.10 & 0.63 & 0.24, 1.62 & 0.3\\
\hspace{1em}other & 0.20 & 0.11, 0.35 & <0.001 & 0.22 & 0.12, 0.41 & <0.001\\
\hspace{1em}south\_asian & 0.79 & 0.44, 1.43 & 0.4 & 0.90 & 0.48, 1.67 & 0.7\\

@@

\textbf{Income * Race} &  &  &  &  &  & \\
\hspace{1em}25000\_59999 * arab\_middle\_eastern & 2.19 & 0.95, 5.05 & 0.067 & 1.85 & 0.68, 4.99 & 0.2\\
\hspace{1em}under\_25000 * arab\_middle\_eastern & 2.95 & 1.39, 6.24 & 0.005 & 3.08 & 1.27, 7.47 & 0.013\\
\hspace{1em}25000\_59999 * black & 1.18 & 0.59, 2.36 & 0.6 & 1.31 & 0.58, 2.98 & 0.5\\
\hspace{1em}under\_25000 * black & 2.84 & 1.46, 5.53 & 0.002 & 3.15 & 1.43, 6.92 & 0.004\\
\hspace{1em}25000\_59999 * east\_asian\_pacific\_islander & 0.97 & 0.44, 2.10 & >0.9 & 0.42 & 0.17, 1.06 & 0.066\\
\hspace{1em}under\_25000 * east\_asian\_pacific\_islander & 1.90 & 0.90, 4.01 & 0.094 & 1.15 & 0.47, 2.84 & 0.8\\
\hspace{1em}25000\_59999 * indigenous & 1.77 & 0.72, 4.32 & 0.2 & 1.33 & 0.46, 3.80 & 0.6\\
\hspace{1em}under\_25000 * indigenous & 1.60 & 0.71, 3.60 & 0.3 & 1.41 & 0.54, 3.72 & 0.5\\
\hspace{1em}25000\_59999 * latin\_american & 0.89 & 0.38, 2.10 & 0.8 & 1.25 & 0.45, 3.45 & 0.7\\
\hspace{1em}under\_25000 * latin\_american & 3.10 & 1.34, 7.21 & 0.009 & 2.81 & 1.04, 7.59 & 0.041\\
\hspace{1em}25000\_59999 * mixed & 0.87 & 0.39, 1.93 & 0.7 & 0.87 & 0.33, 2.33 & 0.8\\
\hspace{1em}under\_25000 * mixed & 1.27 & 0.65, 2.49 & 0.5 & 1.12 & 0.38, 3.33 & 0.8\\
\hspace{1em}25000\_59999 * other & 5.50 & 2.43, 12.5 & <0.001 & 6.96 & 2.67, 18.2 & <0.001\\
\hspace{1em}under\_25000 * other & 4.09 & 2.27, 7.37 & <0.001 & 4.63 & 2.34, 9.13 & <0.001\\
\hspace{1em}25000\_59999 * south\_asian & 1.14 & 0.55, 2.38 & 0.7 & 1.22 & 0.52, 2.87 & 0.7\\
\hspace{1em}under\_25000 * south\_asian & 1.58 & 0.82, 3.05 & 0.2 & 2.01 & 0.93, 4.34 & 0.075\\

@@

\hspace{1em}arab\_middle\_eastern * Central & 0.76 & 0.33, 1.71 & 0.5 & 0.66 & 0.25, 1.69 & 0.4\\
\hspace{1em}black * Central & 0.48 & 0.23, 1.02 & 0.055 & 0.44 & 0.19, 0.99 & 0.046\\
\hspace{1em}east\_asian\_pacific\_islander * Central & 0.84 & 0.38, 1.89 & 0.7 & 0.98 & 0.38, 2.53 & >0.9\\
\hspace{1em}indigenous * Central & 0.60 & 0.24, 1.50 & 0.3 & 0.63 & 0.22, 1.78 & 0.4\\
\hspace{1em}latin\_american * Central & 0.69 & 0.28, 1.71 & 0.4 & 0.66 & 0.22, 1.93 & 0.4\\
\hspace{1em}mixed * Central & 0.63 & 0.30, 1.35 & 0.2 & 0.73 & 0.24, 2.23 & 0.6\\
\hspace{1em}other * Central & 0.98 & 0.49, 1.95 & >0.9 & 0.81 & 0.36, 1.81 & 0.6\\
\hspace{1em}south\_asian * Central & 0.71 & 0.34, 1.47 & 0.4 & 0.55 & 0.25, 1.21 & 0.14\\
\hspace{1em}arab\_middle\_eastern * East & 0.57 & 0.20, 1.63 & 0.3 & 0.43 & 0.13, 1.43 & 0.2\\
\hspace{1em}black * East & 0.84 & 0.37, 1.89 & 0.7 & 0.86 & 0.35, 2.11 & 0.7\\
\hspace{1em}east\_asian\_pacific\_islander * East & 0.82 & 0.30, 2.24 & 0.7 & 0.86 & 0.29, 2.54 & 0.8\\
\hspace{1em}indigenous * East & 0.56 & 0.21, 1.45 & 0.2 & 0.70 & 0.23, 2.11 & 0.5\\
\hspace{1em}latin\_american * East & 0.80 & 0.28, 2.25 & 0.7 & 1.03 & 0.31, 3.40 & >0.9\\
\hspace{1em}mixed * East & 0.70 & 0.31, 1.60 & 0.4 & 0.92 & 0.28, 3.05 & 0.9\\
\hspace{1em}other * East & 0.87 & 0.38, 2.02 & 0.7 & 1.08 & 0.40, 2.91 & 0.9\\
\hspace{1em}south\_asian * East & 0.50 & 0.20, 1.24 & 0.14 & 0.51 & 0.19, 1.42 & 0.2\\
\hspace{1em}arab\_middle\_eastern * West & 1.18 & 0.49, 2.82 & 0.7 & 1.02 & 0.37, 2.77 & >0.9\\
\hspace{1em}black * West & 0.78 & 0.36, 1.67 & 0.5 & 0.77 & 0.32, 1.82 & 0.5\\
\hspace{1em}east\_asian\_pacific\_islander * West & 0.54 & 0.24, 1.21 & 0.14 & 0.52 & 0.20, 1.36 & 0.2\\
\hspace{1em}indigenous * West & 0.45 & 0.19, 1.05 & 0.064 & 0.40 & 0.14, 1.12 & 0.082\\
\hspace{1em}latin\_american * West & 0.99 & 0.39, 2.48 & >0.9 & 0.96 & 0.33, 2.79 & >0.9\\
\hspace{1em}mixed * West & 0.53 & 0.25, 1.10 & 0.088 & 0.37 & 0.12, 1.15 & 0.085\\
\hspace{1em}other * West & 0.55 & 0.27, 1.12 & 0.10 & 0.41 & 0.18, 0.92 & 0.032\\
\hspace{1em}south\_asian * West & 0.50 & 0.24, 1.08 & 0.078 & 0.41 & 0.18, 0.95 & 0.037\\*

@@

There existence of healthcare disparities within Ontario is a topic of
particular interest as it motivated the recent change in the healthcare
system of this region, which a system based on Health Regions in late
2019 in an attempt to address the disparities from the LHIN
model\textsuperscript{\protect\hyperlink{ref-tsasis2012}{30},\protect\hyperlink{ref-dong2022}{31}}.
In this context, analyzing COVID-19 vaccination estimates within the
province is important as they can provide an initial assessment of
variations that might need to be addressed by decision-makers.

Our results indicate that across the most densely populated Health
Regions of Ontario, almost three quarters of the surveyed individuals
reported having received the first dose of the COVID-19 vaccine
(Table~\ref{tbl-descriptive-stats}). It is worth mentioning that
province-wide vaccination rates for the period of interest are somewhat
different from those of the survey, particularly in the case of those 55
years of age and older, which in the survey had a vaccination rate of
72\%, against a rate of 88.4\% reported for the closest age bracket (50
years of age and older) reported by Public Health Ontario at the start
of the period covered by the data (between October 1st, 2021 and
December 12th,
2021)\textsuperscript{\protect\hyperlink{ref-ontario-covid}{39}}. In
this regard, differences are to be expected because the survey
represents a random sample from the population, and therefore, the
sampling process is likely to cause variations between the values from
the survey and province-wide estimates.

We believe that these differences did not have a significant impact in
our analyses, because our results indicate that there were no
significant differences in vaccination odds among the age groups
considered in the survey, in agreement with the overall vaccination
rates reported for Canada, which have been relatively higher when
compared to other high income
countries\textsuperscript{\protect\hyperlink{ref-dube2022}{40}}, and
with vaccination uptake rates across different age groups presented in
other
studies\textsuperscript{\protect\hyperlink{ref-guay2022}{19},\protect\hyperlink{ref-macdonald2021}{41}}.
Moreover, vaccination rates within each age in the dataset are in good
agreement with province-wide estimates (e.g., a rate of 95\% for those
with 61 years of age, Supplementary Table A-6). Additionally, when
overall vaccination rates for the province are disaggregated, it can be
seen that regional differences were present during the period analyzed,
which can be masked by province-wide estimates. For example, the Public
Health Unit of Lambton (a region within the West Health Region) and the
Public Health Unit of Haliburton, Kawartha, and the Pine Ridge District
(an area covered by the East Health Region) reported lower vaccination
rates (78\%) for those 50 years of age and older at the beginning of the
period of interest, whereas other regions had higher vaccination
rates\textsuperscript{\protect\hyperlink{ref-ontario-covid}{39}}. To
this day, differences in vaccination rates within the province are
present, because according to Public Health Ontario, as of March of 2023
some regions have less than 75\% vaccination
rate\textsuperscript{\protect\hyperlink{ref-ontario-covid-map}{42}}.
Overall, these reasons indicate that the estimates obtained from the
data are in good agreement with the trends from the population.

>>>>

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi

@@

The COVID-19 pandemic continues to be a worldwide public health concern.
Although vaccines against this disease were rapidly developed,
vaccination uptake has not ben equal across all the segments of the
population. In particular, it has been shown that there have been
differences in vaccine uptake across different segments of the
population. However, there are also differences in vaccination across
geographical areas, which might be important to consider in the
development of future public health policies against COVID-19. In this
study, we examined the relationship between vaccination status (having
received the first dose of a COVID-19 vaccine), and different
socio-economic and geographical factors. Our results show differences in
vaccination due to race/ethnicity, income, Health Regions (geographical
areas used for health service access in Ontario), and their
interactions. In particular, we show that individuals who identified as
Arab/Middle Eastern, Black, or Latin American, had significantly lower
odds of vaccination than White/Caucasian individuals (ORs and 95\%
CIs=0.31{[}0.14,0.68{]}, 0.32{[}0.17,0.60{]}, 0.27{[}0.11,0.66{]},
respectively), and that individuals with a household income below CAD
25,000 who identified as Arab/Middle Eastern (OR=3.08, 95\%
CI={[}1.27,7.47{]}), Black (OR=3.15,95\% CI={[}1.43,6.92{]}), Latin
American (OR=2.81, 95\% CI={[}1. 04,7.59{]}), or that belonged to other
minority groups (OR=4.63,95\% CI={[}2.34,9.13{]}) had higher odds of
vaccination than individuals from the same racial/ethnic group in higher
income brackets. Finally, we also identified lower odds of vaccination
within certain minority groups in the West Health Region. This study
shows that there is an ongoing need to better understand and address
differences in vaccination uptake across diverse segments of the
population that have been largely impacted by the pandemic.

@@

Within the age groups of survey respondents, the age group between 16-34
years had the highest representation in the survey responses (1,520 or
42.8\% of all responses). Within this age bracket, 73\% of respondents
indicated having received the vaccine, whereas the lowest vaccination
rate was in the bracket of those 55 years of age and above, with 72\%.
The Health Region with highest representation in the survey was Toronto,
accounting for 1,323 entries (37.3\% of the total), with a vaccination
rate of 72\%. Across the three months covered by the survey, the highest
number of entries was in October of 2021, with a total of 1,732
respondents, which corresponded to 49\% of all the survey entries.
Additionally, the proportion of respondents who reported being
vaccinated was similar in all months, ranging between 72\% and 75\%,
with the highest value corresponding to December of 2021.

Regarding race/ethnicity, individuals that identified as White/Caucasian
represented 37\% of all entries (1,312) and had the highest vaccination
uptake with 82\% of them indicating to have received the COVID-19
vaccine. On the other hand, the ethnic group with the lowest number of
entries in the survey was Latin American, with a total of 180, or 5\% of
all entries. Vaccination rates across all minority groups were below the
value reported by White/Caucasians, with the lowest vaccination rate
(60\%) being reported by individuals that identified as Indigenous.

@@

\begin{tabular}{lcc}
\toprule
\textbf{Variable} & \textbf{no}, N = 958 & \textbf{yes}, N = 2,591\\
\midrule
\textbf{Income (CAD)} &  & \\
\hspace{1em}60000 and above & 305 (23\%) & 1,048 (77\%)\\
\hspace{1em}25000-59999 & 253 (28\%) & 636 (72\%)\\
\hspace{1em}under 25000 & 400 (31\%) & 907 (69\%)\\
\textbf{Age Group} &  & \\
\hspace{1em}16-34 & 409 (27\%) & 1,111 (73\%)\\
\hspace{1em}35-54 & 252 (26\%) & 712 (74\%)\\
\hspace{1em}55 and over & 297 (28\%) & 768 (72\%)\\
\textbf{Health Region} &  & \\
\hspace{1em}Toronto & 371 (28\%) & 952 (72\%)\\
\hspace{1em}Central & 224 (28\%) & 580 (72\%)\\
\hspace{1em}East & 135 (23\%) & 448 (77\%)\\
\hspace{1em}West & 228 (27\%) & 611 (73\%)\\
\textbf{Month} &  & \\
\hspace{1em}October & 469 (27\%) & 1,263 (73\%)\\
\hspace{1em}November & 376 (28\%) & 980 (72\%)\\
\hspace{1em}December & 113 (25\%) & 348 (75\%)\\
\textbf{Race} &  & \\
\hspace{1em}White/Caucasian & 233 (18\%) & 1,079 (82\%)\\
\hspace{1em}Arab/Middle Eastern & 76 (36\%) & 138 (64\%)\\
\hspace{1em}Black & 114 (38\%) & 184 (62\%)\\
\hspace{1em}East Asian/Pacific Islander & 69 (23\%) & 234 (77\%)\\
\hspace{1em}Indigenous & 76 (40\%) & 115 (60\%)\\
\hspace{1em}Latin American & 69 (38\%) & 111 (62\%)\\
\hspace{1em}Mixed & 105 (34\%) & 205 (66\%)\\
\hspace{1em}Other & 128 (35\%) & 239 (65\%)\\
\hspace{1em}South Asian & 88 (24\%) & 286 (76\%)\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\end{tabular}
\endgroup{}
\end{table}

@@

\hspace{1em}16-34 & — & — &  & — & — & \\
\hspace{1em}35-54 & 0.93 & 0.77, 1.14 & 0.5 & 0.90 & 0.67, 1.21 & 0.5\\
\hspace{1em}55 and over & 0.74 & 0.61, 0.89 & 0.002 & 0.99 & 0.74, 1.32 & >0.9\\

@@

\textbf{Income (CAD)} &  &  &  &  &  & \\
\hspace{1em}60000 and above & — & — &  & — & — & \\
\hspace{1em}25000-59999 & 0.59 & 0.41, 0.84 & 0.003 & 0.59 & 0.39, 0.88 & 0.010\\
\hspace{1em}under 25000 & 0.41 & 0.29, 0.58 & <0.001 & 0.37 & 0.25, 0.56 & <0.001\\

@@

\hspace{1em}White/Caucasian & — & — &  & — & — & \\
\hspace{1em}Arab/Middle Eastern & 0.24 & 0.12, 0.49 & <0.001 & 0.31 & 0.14, 0.68 & 0.003\\
\hspace{1em}Black & 0.30 & 0.17, 0.54 & <0.001 & 0.32 & 0.17, 0.60 & <0.001\\
\hspace{1em}East Asian/Pacific Islander & 0.73 & 0.36, 1.51 & 0.4 & 1.15 & 0.50, 2.66 & 0.7\\
\hspace{1em}Indigenous & 0.38 & 0.17, 0.82 & 0.014 & 0.45 & 0.20, 1.04 & 0.061\\
\hspace{1em}Latin American & 0.28 & 0.13, 0.59 & <0.001 & 0.27 & 0.11, 0.66 & 0.004\\
\hspace{1em}Mixed & 0.58 & 0.30, 1.11 & 0.10 & 0.63 & 0.24, 1.62 & 0.3\\
\hspace{1em}Other & 0.20 & 0.11, 0.35 & <0.001 & 0.22 & 0.12, 0.41 & <0.001\\
\hspace{1em}South Asian & 0.79 & 0.44, 1.43 & 0.4 & 0.90 & 0.48, 1.67 & 0.7\\

@@

\textbf{Income (CAD) * Race} &  &  &  &  &  & \\
\hspace{1em}25000-59999 * Arab/Middle Eastern & 2.19 & 0.95, 5.05 & 0.067 & 1.85 & 0.68, 4.99 & 0.2\\
\hspace{1em}under 25000 * Arab/Middle Eastern & 2.95 & 1.39, 6.24 & 0.005 & 3.08 & 1.27, 7.47 & 0.013\\
\hspace{1em}25000-59999 * Black & 1.18 & 0.59, 2.36 & 0.6 & 1.31 & 0.58, 2.98 & 0.5\\
\hspace{1em}under 25000 * Black & 2.84 & 1.46, 5.53 & 0.002 & 3.15 & 1.43, 6.92 & 0.004\\
\hspace{1em}25000-59999 * East Asian/Pacific Islander & 0.97 & 0.44, 2.10 & >0.9 & 0.42 & 0.17, 1.06 & 0.066\\
\hspace{1em}under 25000 * East Asian/Pacific Islander & 1.90 & 0.90, 4.01 & 0.094 & 1.15 & 0.47, 2.84 & 0.8\\
\hspace{1em}25000-59999 * Indigenous & 1.77 & 0.72, 4.32 & 0.2 & 1.33 & 0.46, 3.80 & 0.6\\
\hspace{1em}under 25000 * Indigenous & 1.60 & 0.71, 3.60 & 0.3 & 1.41 & 0.54, 3.72 & 0.5\\
\hspace{1em}25000-59999 * Latin American & 0.89 & 0.38, 2.10 & 0.8 & 1.25 & 0.45, 3.45 & 0.7\\
\hspace{1em}under 25000 * Latin American & 3.10 & 1.34, 7.21 & 0.009 & 2.81 & 1.04, 7.59 & 0.041\\
\hspace{1em}25000-59999 * Mixed & 0.87 & 0.39, 1.93 & 0.7 & 0.87 & 0.33, 2.33 & 0.8\\
\hspace{1em}under 25000 * Mixed & 1.27 & 0.65, 2.49 & 0.5 & 1.12 & 0.38, 3.33 & 0.8\\
\hspace{1em}25000-59999 * Other & 5.50 & 2.43, 12.5 & <0.001 & 6.96 & 2.67, 18.2 & <0.001\\
\hspace{1em}under 25000 * Other & 4.09 & 2.27, 7.37 & <0.001 & 4.63 & 2.34, 9.13 & <0.001\\
\hspace{1em}25000-59999 * South Asian & 1.14 & 0.55, 2.38 & 0.7 & 1.22 & 0.52, 2.87 & 0.7\\
\hspace{1em}under 25000 * South Asian & 1.58 & 0.82, 3.05 & 0.2 & 2.01 & 0.93, 4.34 & 0.075\\

@@

\hspace{1em}Arab/Middle Eastern * Central & 0.76 & 0.33, 1.71 & 0.5 & 0.66 & 0.25, 1.69 & 0.4\\
\hspace{1em}Black * Central & 0.48 & 0.23, 1.02 & 0.055 & 0.44 & 0.19, 0.99 & 0.046\\
\hspace{1em}East Asian/Pacific Islander * Central & 0.84 & 0.38, 1.89 & 0.7 & 0.98 & 0.38, 2.53 & >0.9\\
\hspace{1em}Indigenous * Central & 0.60 & 0.24, 1.50 & 0.3 & 0.63 & 0.22, 1.78 & 0.4\\
\hspace{1em}Latin American * Central & 0.69 & 0.28, 1.71 & 0.4 & 0.66 & 0.22, 1.93 & 0.4\\
\hspace{1em}Mixed * Central & 0.63 & 0.30, 1.35 & 0.2 & 0.73 & 0.24, 2.23 & 0.6\\
\hspace{1em}Other * Central & 0.98 & 0.49, 1.95 & >0.9 & 0.81 & 0.36, 1.81 & 0.6\\
\hspace{1em}South Asian * Central & 0.71 & 0.34, 1.47 & 0.4 & 0.55 & 0.25, 1.21 & 0.14\\
\hspace{1em}Arab/Middle Eastern * East & 0.57 & 0.20, 1.63 & 0.3 & 0.43 & 0.13, 1.43 & 0.2\\
\hspace{1em}Black * East & 0.84 & 0.37, 1.89 & 0.7 & 0.86 & 0.35, 2.11 & 0.7\\
\hspace{1em}East Asian/Pacific Islander * East & 0.82 & 0.30, 2.24 & 0.7 & 0.86 & 0.29, 2.54 & 0.8\\
\hspace{1em}Indigenous * East & 0.56 & 0.21, 1.45 & 0.2 & 0.70 & 0.23, 2.11 & 0.5\\
\hspace{1em}Latin American * East & 0.80 & 0.28, 2.25 & 0.7 & 1.03 & 0.31, 3.40 & >0.9\\
\hspace{1em}Mixed * East & 0.70 & 0.31, 1.60 & 0.4 & 0.92 & 0.28, 3.05 & 0.9\\
\hspace{1em}Other * East & 0.87 & 0.38, 2.02 & 0.7 & 1.08 & 0.40, 2.91 & 0.9\\
\hspace{1em}South Asian * East & 0.50 & 0.20, 1.24 & 0.14 & 0.51 & 0.19, 1.42 & 0.2\\
\hspace{1em}Arab/Middle Eastern * West & 1.18 & 0.49, 2.82 & 0.7 & 1.02 & 0.37, 2.77 & >0.9\\
\hspace{1em}Black * West & 0.78 & 0.36, 1.67 & 0.5 & 0.77 & 0.32, 1.82 & 0.5\\
\hspace{1em}East Asian/Pacific Islander * West & 0.54 & 0.24, 1.21 & 0.14 & 0.52 & 0.20, 1.36 & 0.2\\
\hspace{1em}Indigenous * West & 0.45 & 0.19, 1.05 & 0.064 & 0.40 & 0.14, 1.12 & 0.082\\
\hspace{1em}Latin American * West & 0.99 & 0.39, 2.48 & >0.9 & 0.96 & 0.33, 2.79 & >0.9\\
\hspace{1em}Mixed * West & 0.53 & 0.25, 1.10 & 0.088 & 0.37 & 0.12, 1.15 & 0.085\\
\hspace{1em}Other * West & 0.55 & 0.27, 1.12 & 0.10 & 0.41 & 0.18, 0.92 & 0.032\\
\hspace{1em}South Asian * West & 0.50 & 0.24, 1.08 & 0.078 & 0.41 & 0.18, 0.95 & 0.037\\*

@@

The existence of healthcare disparities in Ontario motivated the recent
change in the healthcare system of the province, which changed the LHIN
model for a Health Region model in late
2019\textsuperscript{\protect\hyperlink{ref-tsasis2012}{30},\protect\hyperlink{ref-dong2022}{31}}.
In this context, analyzing COVID-19 vaccination estimates between the
Health Regions can serve as an indicator of ongoing intra-provincial
disparities that may need to be addressed to ensure that the Health
Region model is able to improve health access for the inhabitants of
Ontario, which faces unique challenges due to its condition as the most
populated and the most ethnically diverse province of Canada.

Our results indicate that across the most densely populated Health
Regions of Ontario, almost three quarters of surveyed individuals
reported to have received the first dose of the COVID-19 vaccine
(Table~\ref{tbl-descriptive-stats}). It is worth mentioning that
province-wide vaccination rates for the period of interest are somewhat
different from those of the survey, particularly in the case of those 55
years of age and older, which in the survey had a vaccination rate of
72\%, against a rate of 88.4\% reported for the closest age bracket (50
years of age and older) reported by Public Health Ontario at the start
of the period covered by the data (between October 1st, 2021 and
December 12th,
2021)\textsuperscript{\protect\hyperlink{ref-ontario-covid}{39}}. In
this case, differences between the survey and province-wide estimates
are to be expected as the data from survey represents a random sample
from the overall population.

However, this variation did not lead to discrepant results, as the
estimates from the model indicate that no significant differences in
vaccination odds were identified among the age groups analyzed, in
agreement with both overall vaccination rates reported for Canada, which
have been relatively higher when compared to other high income
countries\textsuperscript{\protect\hyperlink{ref-dube2022}{40}}, and
with vaccination uptake rates across different age groups presented in
other
studies\textsuperscript{\protect\hyperlink{ref-guay2022}{19},\protect\hyperlink{ref-macdonald2021}{41}}.
In other words, although vaccination rates obtained from the survey were
slightly lower than the provincial estimates, these values still
represented a valid approximation; this notion is reinforced by the
consistency in the proportion of vaccination rates
(Table~\ref{tbl-descriptive-stats}) and vaccination odds
(Table~\ref{tbl-model}) across the period covered by the survey, which
follow the vaccination rates from Public Health Ontario and which
indicate that due to the relatively high coverage achieved in the
population at that point, there were no abrupt shift in the trends,
which increased by around 3\% across all age groups during the three
months (October, November, and December of
2021\textsuperscript{\protect\hyperlink{ref-ontario-covid}{39}}).
Moreover, there was good agreement between vaccination rates within each
age in the raw dataset and province-wide estimates (e.g., a rate of 95\%
for those with 61 years of age, Supplementary Table A-6, which is
similar to the value reported by Public Health Ontario). It is also
important to mention that regional differences can be masked by overall
estimates, as when overall vaccination rates for the province (from
Public Health Ontario) are disaggregated, it can be seen that regional
differences during the period analyzed existed. For example, the Public
Health Unit of Lambton (a region within the West Health Region) and the
Public Health Unit of Haliburton, Kawartha, and the Pine Ridge District
(an area covered by the East Health Region) reported lower vaccination
rates (78\%) for those 50 years of age and older at the beginning of the
period of interest, in contrast with other regions that had vaccination
rates above
80\%\textsuperscript{\protect\hyperlink{ref-ontario-covid}{39}}. To this
day, differences in vaccination rates within the province continue, as
according to Public Health Ontario, as of March of 2023 some regions
still have less than 75\% vaccination
rate\textsuperscript{\protect\hyperlink{ref-ontario-covid-map}{42}}.
